|

### 2021-12-15 03-Chp-Systematic-Review-Methods.Rmd
SMall edits

Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question. Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.

@@

This chapter presents the methods used to perform a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes. In addition, the review examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes. The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading).
:::

@@

This analysis sought to address two specific aims. Firstly, as discussed in the introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship between lipids and dementia exist. These include randomised controlled trials, observational studies of different design, and Mendelian randomisation studies. However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types. Collating these diverse evidence sources is important, as, if the observed association between lipids and dementia is constant across them, it increases our confidence in the association. As such, the primary aim of this analysis was to systematically review all available literature describing prospective analyses, regardless of study design.

Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but can report relevant unpublished analyses. As a sensitivity analysis to the review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).

Given the size of the review, I have separated the methods and results into two chapters for ease of reading. This chapter details the methodology used, while Chapter \@ref(sys-rev-results-heading) presents the results.

@@

In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes. Due to the scale of the project, this review was performed in conjunction with a team of secondary reviewers (see Acknowledgements and Author Declaration in the front matter).

@@

I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase in a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides). I also aimed to include studies examining the effect of lipid-regulating agents (LRA) as a source of indirect evidence. LRA are treatments used to modify blood lipids levels, and common examples include statins, fibrates, and ezetimibe.

@@

Eligible studies screened participants for dementia at baseline and excluded any prevalent cases. Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate. No limits were placed on the sample size of included studies. Eligible studies defined dementia outcomes according to recognised criteria. Examples of acceptable criteria included the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the sole exception to this, as it was assumed that health care professionals employed their own expertise when entering the outcome into the EHR.

Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain relevant additional information not available from the abstract. No limitations were imposed on publication status, date, venue or language.

@@

Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though case-control studies where historical records are used to determine the exposure status were eligible for inclusion. Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measure change in continuous cognitive measures (e.g. MoCA score) without an attempt to map these scores to ordinal groups (e.g. no dementia/dementia).[@tennant2021] Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.

Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) and studies where there was no screening for dementia at baseline were excluded. An exception to the latter criteria was made if the sample was initially assessed in mid-life (i.e. below the age of 50) were excluded. Additionally, studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arm were excluded. For example, a study examining exercise + statins versus statins alone would be excluded, but a study examining exercise + statins vs exercise alone would be eligible as the effect of statins can be estimated. Finally, studies using a dietary intervention, for example an omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet. Note that this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.

@@

I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records"). The following databases were searched in June 2019 from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection. As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases). The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed. A high-level outline of the strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy. Should be able to loop through search strategy results. -->

@@

<!----------------------------------------------------------------------------->
(ref:searchOverview-caption) __Summary of systematic search by topic__ - The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).

@@

When searching the bibliographic databases, study design filters (Lines 9-11 in Table \@ref(tab:searchOverview-table)) were employed to try to reduce the screening load. To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.

<!-- TODO need to comment on this feed-back process, or remove -->

@@

Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. In addition, the abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range --> Finally, the reference lists of included studies were searched by hand, while forward and reverse citation searching ("snowballing") was performed using Google Scholar.[@greenhalgh2005; @wohlin2014]

@@

Following de-duplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote and Rayyan. Endnote is a citation management tool,[@hupe2019] and Rayyan is a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. Additionally, I re-screened the same ~10% sample with 3 month lag to assess intra-rater consistency.

@@

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does. [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic. The formulae used to calculate the coefficient are given in Appendix \@ref(appendix-gwet).

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrates an issue with the screening process (defined as an AC1 of less than 0.9), it indicates the need for a larger proportion of records to be dual-screened.

@@

* Article metadata: year of publication, author, journal)
* Study characteristics: study location, data source, exposure, outcomes, diagnostic criteria used)
* Patient characteristics: age, sex, baseline cognition scores, baseline education scores
* Results: exposure, outcome, effect measure, effect estimate, error estimate, p-value).

@@

As part of the data extraction process, multiple records resulting from a single analysis were included and grouped into single units, hereafter called studies. This was most common in cases where multiple records reported on the same analysis but at different time points. In this case, the result corresponding to the longest follow-up was used. Grouping records into studies builds out the most comprehensive account of a given analysis by incorporating information from all available records.

@@

where $N_i$, $M_i$ and $SD_i$ denote the number of participants, mean and standard deviation in the $i$th subgroup. This approach was implemented in a systematic manner, with the raw group data being extracted and a cleaning script employed to combine the groups for analysis.

@@

where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.[@rugge2011] The choice of _mg/dL_ was influenced by the widely-used categories of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).

@@

Where additional data, not included in the report of an analysis, were required either for data extraction or risk-of-bias assessment, the corresponding author of the study was contacted. This approach was taken due to the potentially large impact of additional information obtained through contact with study authors on the results of the review.[@reynders2019]

@@

A key aim of the review presented here is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis). To enable this triangulation exercise, detailed and structured risk-of-bias assessment formed an important part of this review.

There has been a recent movement within the evidence synthesis community away from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study. Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]

This move was prompted by an unclear definition of methodological quality which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools. <!-- TODO CITATION NEEDED --> As part of this shift, the focus moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order. <!-- TODO CITATION NEEDED --> Finally, the new tools tools move from assessing bias at the study level to considering separately each individual numerical result reported.  For example, a study may report on the efficacy of an intervention at six months and two years follow-up. In this case, the proportion of missing outcome data may not be an issue at six months but may introduce bias after two years of follow-up. In this case, assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.

In this review, domain-based tools were used to assess the risk of bias for each result in each included study. The study design-specific tools are introduced and discussed in more detail in the following sections.

@@

Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains:

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains:

@@

While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] it was insufficiently developed at the time the risk-of-bias assessments for this review were performed. Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of risk of bias as ROBINS-I, were made at the domain level. The motivation for using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS. Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs as part of this review.

@@

At present, no formalised risk-of-bias assessment tool for Mendelian randomisation studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies.[@spiga2021] Advanced results from this review were obtained from contact with the review authors. A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification. Acceptable judgements for each of the five domains in the tool were "low", "moderate" and "high" risk of bias.

@@

In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level. This assessment examines evidence missing due to selective non-reporting as distinct from the selective reporting of a single result from multiple planned analyses. The assessment was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.

@@

I used a random-effects model in all meta-analyses.[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$. The result in the $i$th study is denoted as $y_i$. The weight assigned to this result is then given as the inverse of the variance of that result ($v_i$) plus the estimate of between-result variance ($\tau^2$):

@@

Results included in each meta-analysis were stratified into subgroups on the basis of the overall risk of bias judgement, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate. Finally, where at least 10 results are available, a test of subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).[@deeks2019] All models were implemented using the `metafor` R package.[@R-metafor]

@@

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups. In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels.

<!-- TODO Maybe rephrase last sentence -->

@@

Where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics. _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results. Syntheses with greater than 10 results were assessed for heterogeneity across these covariates.[@deeks2019]

Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and formally using Egger's regression test.[@sterne2011]

@@

Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As part of the initial descriptive synthesis, the location of each individual study contributing to the evidence base was visualised on a world map.

One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond. This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool. Unless otherwise stated in the figure caption, only a single effect measure (hazard ratio/odds ratio/etc) is represented in the forest plot.

@@

Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)). As an adjunct analysis to this review, meta-analyses including a preprint result were re-analysed using a fixed effect model. The weight assigned to the preprinted result was extracted and used to assess the additional evidential value provided by the preprint. In addition, in meta-analysis including at least one preprinted result, I assessed the impact of including the preprinted results on the summary estimate using a leave-one-out approach.

<!-- COMMENT You need to state a priori in what objective way you can judge if pre-prints do or do not have added value -->

Additionally, I performed a follow-up analysis, allowing for a a two-year lag, to investigate whether identified preprints had been subsequently published (in which case preprints provided a snapshot into the future, and a systematic review update would capture the published version of the preprint) or not (in which case preprints provide a distinct evidence source to conventional bibliographic databases).

@@

* In this chapter, I have presented the methods underpinning a comprehensive systematic review of the existing literature on the association of dementia incidence with blood lipids and lipid-regulating agents.

* I have detailed how this review will find, extract, critically assess and synthesize the results of existing studies. Additionally, I have highlighted how this review will examine the impact of including preprinted results, as enabled by the research tool presented in the previous chapter.

* In the following chapter, I present the results of this review, and detail how the identified evidence is used throughout the remainder of the thesis.

>>>>

Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to a research question. Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.

@@

This chapter presents the methods used to perform a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes. In addition, the review included studies that examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes. The results of this systematic review are presented in Chapter \@ref(sys-rev-results-heading).
:::

@@

This analysis sought to address two specific aims. Firstly, as discussed in the introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship between lipids and dementia exist. These include randomised controlled trials, observational studies of different design, and Mendelian randomisation studies. However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipid levels with dementia outcomes across these distinct evidence types. Collating these diverse evidence sources is important because, if the observed association between lipids and dementia is constant across them, it increases our confidence in the association. As such, the primary aim of this analysis was to systematically review all available literature describing prospective analyses, regardless of study design.

Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but can report relevant unpublished analyses. As a sensitivity analysis to the review presented in this chapter, I sought to quantify the additional evidential value of relevant preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).

Given the size of the review, I have split its reporting across two separate chapters for ease of reading. This chapter details the methodology used, while Chapter \@ref(sys-rev-results-heading) presents the results.

@@

In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes. Due to the scale of the project, this review was performed in conjunction with a team of secondary reviewers (see Acknowledgements in the front matter).

@@

I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as a binary hypercholesterolemia variable or by category/1-standard-deviation increase in a specific lipid fraction. The fractions considered by this review were namely total cholesterol (TC), high-density lipoprotein cholesterol (HDL), low-density lipoprotein cholesterol (LDL) and triglycerides (TG). I also aimed to include studies examining the effect of lipid-regulating agents (LRA) as a source of indirect evidence. LRA are treatments used to modify blood lipids levels, and common examples include statins, fibrates, and ezetimibe.

@@

Eligible studies screened participants for dementia at baseline and excluded any prevalent cases. Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline. Eligible studies defined dementia outcomes according to recognised criteria. Examples of acceptable criteria included the International Classification of Diseases (ICD),[@organizationwho1993] the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] and the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were an exception to this, as it was assumed that health care professionals employed their own expertise when entering the outcome into the EHR.

Studies of any duration were included, and no limits were placed on the sample size of included studies. Finally, conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain relevant additional information not available from the abstract. No limitations were imposed on publication status, date, venue or language.

@@

Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though case-control studies where historical records are used to determine the exposure status were eligible for inclusion. Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measured change in continuous cognitive measures (e.g. Montreal Cognitive Assessment (MoCA) score) without an attempt to map these scores to ordinal groups (e.g. no dementia/dementia).[@tennant2021] Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.

Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) were excluded. Additionally, studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arm were excluded. For example, a study examining exercise + statins versus statins alone would be excluded, but a study examining exercise + statins vs exercise alone would be eligible as the effect of statin use can be estimated. Finally, studies using a dietary intervention, for example an omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet. Note that this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.

@@

I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records"). The following databases were searched in June 2019 from inception onwards: MEDLINE, Embase, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection. Given that the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).

The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms, incorporating input from an information specialist. The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for use in MEDLINE before being adapted to the other bibliography databases listed. A high-level outline of the strategy is presented in Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy. Should be able to loop through search strategy results. -->

@@

<!----------------------------------------------------------------------------->
(ref:searchOverview-caption) __Summary of systematic search by topic__ - The full search strategy for each databases searched, including all search terms and the number of hits per term, is presented in Appendix \@ref(appendix-search-strategy).

@@

When searching the bibliographic databases, study design filters (Lines 9-11 in Table \@ref(tab:searchOverview-table)) were employed to try to reduce the screening load. I confirmed that the study design filters were not excluding potentially relevant records by screening a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)).

@@

Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, and theses were accessed using the Open Access Theses and Dissertations portal. In addition, the abstract lists of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. Finally, the reference lists of included studies were searched by hand, while forward and reverse citation searching ("snowballing") was performed using Google Scholar.[@greenhalgh2005; @wohlin2014]

@@

Following de-duplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote and Rayyan. Endnote is a citation management tool,[@hupe2019] and Rayyan is a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. Additionally, I re-screened the same ~10% sample with three month lag to assess intra-rater consistency.

@@

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This approach was chosen over other measures such as percent agreement because it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does. [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic. The formulae used to calculate AC1 are given in Appendix \@ref(appendix-gwet).

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrated an issue with the screening process (defined as an AC1 of less than 0.9), it indicated the need for a larger proportion of records to be dual-screened.

@@

* Article metadata: year of publication, author, journal
* Study characteristics: study location, data source, exposure, outcomes, diagnostic criteria used
* Patient characteristics: age, sex, baseline cognition scores, baseline education scores
* Results: exposure, outcome, effect measure, effect estimate, error estimate, p-value

@@

As part of the data extraction process, multiple records resulting from a single analysis were included and grouped into single units, hereafter referred to as studies. This was most common in cases where multiple records reported on the same analysis but at different time points. In this case, the result corresponding to the longest follow-up was used. Grouping records into studies builds out the most comprehensive account of a given analysis by incorporating information from all available records.

@@

where $N_i$, $M_i$ and $SD_i$ denote the number of participants, mean and standard deviation in the $i$th subgroup, respectively. This approach was implemented in a systematic manner, with the raw group data being extracted and a cleaning script employed to combine the groups for analysis.

@@

where $Z = 38.67$ when converting total cholesterol, LDL-c and HDL-c measures, and $Z = 88.57$ when converting triglyceride measures.[@rugge2011] The choice of _mg/dL_ was influenced by the widely-used categories of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).

@@

Where additional data not reported by a study were required either for data extraction or risk-of-bias assessment, the corresponding author of the study was contacted. This approach was taken due to the potentially large impact of additional information obtained through contact with study authors on the results of the review.[@reynders2019]

@@

A key aim of the review presented here is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(intro-triangulation) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis). To enable this triangulation exercise, detailed and structured risk-of-bias assessments formed an important part of this review.

There has been a recent movement within the evidence synthesis community away from examining _methodological quality_ towards assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study. Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]

This move was prompted by an unclear definition of methodological quality which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools. As part of this shift, the focus moved from checklists and score-based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order. Additionally, the new tools move from assessing bias at the study level to considering each individual numerical result separately.  For example, a study may report on the efficacy of an intervention at six months and two years follow-up. In this case, the proportion of missing outcome data may not be an issue at six months but may introduce bias after two years of follow-up. In this case, assigning a single risk-of-bias judgement to the study as a whole would mask the different biases applicable to each unique result.

In this review, domain-based tools were used to assess the risk of bias for each result in each included study. The study-design-specific tools are introduced and discussed in more detail in the following sections.

@@

Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] This tool assesses the risk of bias across five domains:

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assesses the risk of bias across seven domains:

@@

While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] it was insufficiently developed at the time the risk-of-bias assessments were performed. Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of risk of bias as ROBINS-I, were made at the domain level. The motivation for using this tool above other established tools - such as the Newcastle-Ottowa scale (NOS)[@wells2000] - was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS. Secondly, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs considered by this review.

@@

At present, no formalised risk-of-bias assessment tool for Mendelian randomisation studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the tool developed by Mamluk _et al_ for use in their own review.[@mamluk2020] This tool was identified through a meta-review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies,[@spiga2021] advanced results of which were obtained through personal communication with the authors. A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic confounding, other confounding, pleiotropy and population stratification. Acceptable judgements for each of the five domains in the tool were "low", "moderate" and "high" risk of bias.

@@

In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the synthesis level. This assessment examines evidence missing due to selective non-reporting as opposed to the selective reporting of a single result from multiple planned analyses. The assessment was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.

@@

I used a random-effects model in all meta-analyses.[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$. The result in the $i$th study is denoted as $y_i$. The weight ($w_i$) assigned to this result is then given as the inverse of the variance of that result ($v_i$) plus the estimate of between-result variance ($\tau^2$):

@@

Results included in each meta-analysis were stratified into subgroups on the basis of the overall risk-of-bias judgement. Summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate. Finally, where at least 10 results are available, a test of subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).[@deeks2019] All models were implemented using the `metafor` R package.[@R-metafor]

@@

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups. In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels.

@@

Where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics. _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results. Syntheses with greater than 10 results were assessed for heterogeneity across these covariates.[@deeks2019] I also investigated the potential for small study effects (of which publication bias is one potential cause) in syntheses with greater than 10 results, both visually using funnel plots and formally using Egger's regression test.[@sterne2011]

@@

Evidence maps are a useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As part of the initial descriptive synthesis, the location of each individual study contributing to the evidence base was visualised on a world map.

One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the RoB 2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis, as assessed using the RoB-ME tool, is shown beside the overall summary diamond. This tool was developed as an adjunct to this thesis,[@mcguinness2020robvisPaper] and summary of its functionality can be found in Appendix \@ref(appendix-robvis). Unless otherwise stated in the figure, only a single effect measure (hazard ratio/odds ratio/etc) is represented in a given forest plot.

@@

Preprints are considered a valuable evidence source within this thesis (see Section \@ref(diverse-sources-preprints)). As an adjunct analysis to this review, meta-analyses including a preprint result were re-analysed using a fixed effect model. The weight assigned to the preprinted result was extracted and used to assess the additional evidential value provided to the synthesis by the preprint. In addition, I assessed the impact of including the preprinted results on the summary estimate, using a leave-one-out approach.

Finally, I performed a follow-up analysis, allowing for a a two-year lag, to investigate whether included preprints had been subsequently published (in which case preprints provided a snapshot into the future, and a systematic review update would capture the published version of the preprint) or not (in which case preprints provided a distinct evidence source to conventional bibliographic databases).

@@

* In this chapter, I have presented the methods underpinning a comprehensive systematic review of the existing literature on the association of dementia incidence with blood lipid levels and lipid-regulating agents.

* I have detailed how this review found, extracted, critically assessed and synthesized the results of existing studies. Additionally, I have highlighted how this review examined the impact of including preprinted results, as enabled by the research tool presented in the previous chapter.

* In the following chapter, I present the results of this review, and detail how the evidence identified is used throughout the remainder of the thesis.

### 2021-12-15 06-Chp-IPD-Analysis.Rmd
SMall edits

<!-- TODO Need quote for here -->

@@

<!-- TODO Finish lay summary -->

<!-- At the same time, I will write to authors to obtain anonymised data on individual participants. The data from each study will be combined using a technique known as individual participant data (IPD) meta-analysis. This will allow me to examine if the relationship between lipids in dementia depends on any patient characteristics (e.g. sex or age). -->

Individual participant data (IPD) meta-analyses are a special type of meta-analysis
in which the authors of relevant studies are contacted with requests to access the raw data on each participant in the original study. This approach is different to the meta-analyses presented in the previous chapter, which used published summary results.

@@

In order to examine the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables. However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided the requested access.

@@

#### Comparison with previous analysis

>>>>

@@

This chapter examines the raw data pertaining to participants in previously published, relevant studies, a method of analysis called Individual Participant Data (IPD) meta-analysis. It uses this data to investigate the relationship between lipid levels and dementia risk, which is unique from the previous chapter because that chapter used published results rather than individual-level data.

@@

I applied for access to `r n_applied$total` unique data sources for this analysis, however, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided the requested data.

@@

#### Comparison with a previous analysis
